---
title: "tabelog_bayes"
output: html_document
date: "2025-04-12"
---

##Tabelog - Bayesian Modeling

```{r setup, include=FALSE}
library(brms)
library(caret)

set.seed(123)
```

```{r}
# read data
data <- read.csv("./data/tabelog_tokyo_data.csv")

# categorical factoring for genre
genre_levels <- c(
  "chinese", "curry", "italian", "izakaya", "japanese", "korea",
  "pizza", "ramen", "seafood", "sushi", "sweets", "syabusyabu",
  "udon", "washoku", "yakiniku"
)
data$genre <- factor(data$genre, levels = genre_levels)

# if restaurant doesn't have daytime_price
# copy over nighttime price
data$daytime_price_low[is.na(data$daytime_price_low)] <- data$nighttime_price_low[is.na(data$daytime_price_low)]
data$daytime_price_high[is.na(data$daytime_price_high)] <- data$nighttime_price_high[is.na(data$daytime_price_high)]

# standardize & scaling
numerical_features <- c(
  "review_count", "daytime_price_low", "daytime_price_high",
  "nighttime_price_low", "nighttime_price_high", 
  "photo_count", "like_count", "bookmark_count"
)

scaled_features <- scale(data[, numerical_features])
data_scaled <- as.data.frame(scaled_features)

data_scaled$score <- data$score
data_scaled$genre <- data$genre

# train test split (80-20)
train_indices <- createDataPartition(data_scaled$score, p = 0.8, list = FALSE)
Xtrain <- data_scaled[train_indices, ]
Xtest <- data_scaled[-train_indices, ]
```

#Bayesian Linear Model (Gaussian):

```{r}
prior_gaus <- default_prior(score ~ review_count + daytime_price_low + daytime_price_high +
                              nighttime_price_low + nighttime_price_high + 
                              photo_count + like_count + bookmark_count,
                            data = Xtrain,
                            family = gaussian())

tabelog_brm <- brm(score ~ review_count + daytime_price_low + daytime_price_high +
                     nighttime_price_low + nighttime_price_high + 
                     photo_count + like_count + bookmark_count,
                   data = Xtrain,
                   family = gaussian(),
                   chains = 4,
                   iter = 10000,
                   warmup = 1800,
                   prior = prior_gaus)
```

```{r}
plot(tabelog_brm)
```

```{r}
summary(tabelog_brm)
```

```{r}
bayes_R2(tabelog_brm)
```

```{r}
preds <- posterior_predict(tabelog_brm, newdata = Xtest)

means <- colMeans(preds)
trues <- Xtest$score

cor(means, trues)
```

#Bayesian Beta Regression Model (Beta):

```{r}
#scaling 'score' to be between 0 and 1
score_scaled <- data$score / 5

data_scaled$score <- score_scaled

# train test split (80-20)
train_indices <- createDataPartition(data_scaled$score, p = 0.8, list = FALSE)
Xtrain <- data_scaled[train_indices, ]
Xtest <- data_scaled[-train_indices, ]
```

```{r}
prior_beta <- default_prior(score ~ review_count + daytime_price_low + daytime_price_high + 
                              nighttime_price_low + nighttime_price_high + 
                              photo_count + like_count + bookmark_count,
                            data = Xtrain,
                            family = Beta())

tabelog_brm_beta <- brm(score ~ review_count + daytime_price_low + daytime_price_high +
                     nighttime_price_low + nighttime_price_high + 
                     photo_count + like_count + bookmark_count,
                     data = Xtrain,
                     family = Beta(),
                     chains = 4,
                     iter = 10000,
                     warmup = 1800,
                     prior = prior_beta)
```

```{r}
plot(tabelog_brm_beta)
```

```{r}
summary(tabelog_brm_beta)
```

```{r}
bayes_R2(tabelog_brm_beta)
```

```{r}
preds <- posterior_predict(tabelog_brm_beta, newdata = Xtest)

means <- colMeans(preds)
trues <- Xtest$score

cor(means, trues)
```

#Predicting Best Restaurants for a User:
Based on a user-inputted review of desired features of a restaurant, find 5 most similar restaurants to recommend.

```{r}
cosine_similarity <- function(a, b) {
  sum(a * b) / (sqrt(sum(a^2)) * sqrt(sum(b^2)))
}
```

```{r}
# user-inputted review of desired features
# standardized values - lower = cheaper
fake_review <- data.frame(
  review_count = 10,
  daytime_price_low = -0.5,   # standardized lower value = cheaper
  daytime_price_high = 0.8,
  nighttime_price_low = -0.5,
  nighttime_price_high = 0.8,
  photo_count = -0.2,
  like_count = 0.1,
  bookmark_count = 0.1
)

# user-inputted desired genre
fake_genre <- "syabusyabu"

# only include user desired genre
user_genre <- data$genre == fake_genre
data_genre <- data[user_genre, ]
data_scaled_genre <- data_scaled[user_genre, ]

# convert data of restaurants to matrix of numerical features
data_matrix <- as.matrix(data_scaled_genre[, numerical_features])

# convert user review to vector
fake_vector <- as.numeric(fake_review[1, numerical_features])

# cosine similarities between each restaurant and user review
similarities <- apply(data_matrix, 1, function(row) cosine_similarity(row, fake_vector))

# predict score of restaurant using model
pred_scores <- posterior_predict(tabelog_brm_beta, newdata = data_scaled_genre)
expected_ratings <- colMeans(pred_scores)

# top 5 most similar restaurants to user review
top5 <- order(similarities, decreasing = TRUE)[1:5]
top5restaurants <- data_genre[top5, ]
top5restaurants$similarity <- similarities[top5]
top5restaurants$pred_score <- expected_ratings[top5]
```

Finding most similar restaurants, according to cosine similarity scores:

```{r}
print(top5restaurants[, c("store_name", "genre", "score", "pred_score", "similarity")])
```

```{r}
# top 5 highest rated restaurants to user review
top5_score <- order(expected_ratings, decreasing = TRUE)[1:5]
top5restaurants_score <- data_genre[top5_score, ]
top5restaurants_score$similarity <- similarities[top5_score]
top5restaurants_score$pred_score <- expected_ratings[top5_score]
```

Finding highest predicted scored restaurants:

```{r}
print(top5restaurants_score[, c("store_name", "genre", "score", "pred_score", "similarity")])
```